Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}). 
    % The layout is similar to Figure \ref{fig:abundance-evolution-yields}. 
    Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius. A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$. {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
    \label{fig:abundance-evolution-params}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}). Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius. A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$ over time, and the black squares plot the median stellar abundance in in {2 Gyr}-wide age bins. The red line and points plot the median abundance for APOGEE stars in each age bin, and the shaded regions represent the 16th--84th abundance percentiles. Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$ and a higher mass-loading factor $\eta_\odot=0.6$. {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
    \label{fig:abundance-evolution-params}
\end{figure*}
